\LARGE \bf The TransHumUs project for the French Pavilion \\ at La Biennale di Venezia 2015

### 2015-08-26 docs/article.tex
ça commence douuucement

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

    TODO

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{When robotics meets art}
\subsection{The transHumUs project of Céleste Boursier-Mougenot}
vue d’artiste
C/C institut français en anglais
\subsection{The robotics interpretation}
interpretation → discours sur le mouvement

\section{The robotic project}
\subsection{Specifications}
(en relation avec l’artiste)

* feedback sur métabolisme
* arbre de 3t
* holonomie
* silence
* lenteur
* couverture spatiale
* coordination

\subsection{Technical solutions}
* sondes Granier
* AGV tri-tourelles
* localisation absolue

\subsection{Architecture for the generation of motion}
* Présentation générale (scéma octogone avec le CIR)
* Schéma bloc
* captures d’écran du simulateur

@@

* sondes granier
* AGV désossé
* photo de pose des balises dans l’arbre
* arbre en acheminement

@@

   %\begin{figure}[thpb]
      %\centering
      %\framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
%}}
      %%\includegraphics[scale=1.0]{figurefile}
      %\caption{Inductance of oscillation winding on amorphous
       %magnetic core versus DC bias magnetic field}
      %\label{figurelabel}
   %\end{figure}

@@

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

>>>>

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{When robotics meets art}
\subsection{The transHumUs project of Céleste Boursier-Mougenot}

\begin{figure}[thpb]
    \centering
    \includegraphics[width=\linewidth]{img/vue_artiste.jpg}
    \caption{Artist's Impression}
    \label{artists_impression}
\end{figure}

C/C institut français en anglais

\subsection{The robotics interpretation}

interpretation → discours sur le mouvement

\section{The robotic project}
\subsection{Specifications}

(en relation avec l’artiste)

\begin{itemize}
    \item feedback sur métabolisme
    \item arbre de 3t
    \item holonomie
    \item silence
    \item lenteur
    \item couverture spatiale
    \item coordination
\end{itemize}

\subsection{Technical solutions}

\begin{itemize}
    \item sondes Granier
    \item AGV tri-tourelles
    \item localisation absolue
\end{itemize}

\subsection{Architecture for the generation of motion}

\begin{itemize}
    \item Présentation générale (schéma octogone avec le CIR)
    \item Schéma bloc
    \item captures d’écran du simulateur
\end{itemize}

@@

\begin{itemize}
    \item sondes granier
    \item AGV désossé
    \item photo de pose des balises dans l’arbre
    \item arbre en acheminement
\end{itemize}

@@

@@

%References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
